### 2018-07-04 dissertation/1-intro/chapter1.tex
Updated chapter 2

%\section{Document organization}
The remainder of this document is organized as follows. \Cref{chap:complexnetworks} explains the broad study of complex networks and the importance of trust in technological and social networks.
Then, \Cref{chap:vanets} goes into details regarding VANETs and the importance of trust solutions in the field, presenting previous studies made on the subject.
\Cref{chap:truman} describes the goals of TruMan, its underlying hypothesis and the work done to achieve those goals, as well as the previously existing algorithms which form parts of TruMan.
Next, \Cref{chap:simulations} explains the tools used to validate TruMan's functionality and presents the results of the experiments that were performed.
Finally \Cref{chap:conclusion} presents the final thoughts on the project and concludes this document.

>>>>

%\section{Document organization}
The remainder of this document is organized as follows. \Cref{chap:complexnetworks} explains the broad study of complex networks and the importance of trust in social and technological networks, then goes into details regarding VANETs and the importance of trust solutions in the field, presenting previous studies made on the subject.
\Cref{chap:truman} describes the goals of TruMan, its underlying hypothesis and the work done to achieve those goals, as well as the previously existing algorithms which form parts of TruMan.
Next, \Cref{chap:simulations} explains the tools used to validate TruMan's functionality and presents the results of the experiments that were performed.
Finally, \Cref{chap:conclusion} presents the final thoughts on the project and concludes this document.

### 2018-07-04 dissertation/2-complexnetworks/chapter2.tex
Updated chapter 2

\chapter{Complex Networks and Trust}
\label{chap:complexnetworks}

%Often, the term ``network'' is associated only with computer

>>>>

\chapter{Background and Related Work}
\label{chap:complexnetworks}

In order to develop a new trust management scheme for vehicular networks, a review of the study of networks as a whole is required.
This chapter introduces the concept of complex networks, digging into the meaning and importance of trust in the cases of social networks and technological networks.
Then, vehicular ad-hoc networks are explained in details, with the current state of the art, unique properties compared to other networks, desired properties for a vehicular network trust model and details on the most relevant works in the subject.

\section {Complex Networks}
%Often, the term ``network'' is associated only with computer

### 2018-07-04 dissertation/3-vanets/chapter3.tex
Updated chapter 2

\chapter{Trust in Vehicular Ad-hoc Networks}
\label{chap:vanets}

@@

In traditional networks (ad-hoc or not), routing protocols usually use the topology to choose where to forward packets; in other words, the primary metric used is the number of hops required to reach the destination.
This metric is not as useful in vehicular networks, since the high mobility causes the topology to change frequently.
Instead, most VANET routing protocols use geographical coordinates to forward packets \citep{saini2015close}, that is, the physical distance between two nodes is used as the primary metric.
The implication is that, even if a packet requires more hops to reach its destination, it will always be traveling the generally correct direction.

@@

\section{Special properties of VANETs}
\label{section:properties}
%As was described above, VANETs are a special type of MANETs, which in turn are technological networks.
%However, 
VANETs feature several unique properties which distinguish them, and the behavior of its members, from other types of networks \citep{yousefi2006vehicular}.
Some of these properties include:

@@

\section{Trust in VANETs}
\label{section:trustvanet}
Like in other types of networks, the proper functioning of a VANET depends on the reliability of the vehicles (nodes) which participate in it.
If a node is malicious or faulty, it can spread incorrect data that may compromise the network's utility.
Once the concept of VANETs was established, researchers have been attempting to predict ways in which malicious users might use the network to their advantage.
Examples include triggering false alarms about inexistent accidents, lying about the average speed in a road to make it less desirable for others, and falsifying geolocation data to exploit location-based routing algorithms.
Therefore, the concept of trust must be established in the vehicular network context, allowing for nodes to judge the validity of information transmitted by others and share those conclusions with other nodes.

%[details of security and safety issues in VANETs that can be diminished by trust]
\section{Desired properties for VANET trust models}
\label{section:properties}

@@

\section{Existing trust models for VANETs}

@@

\citep{dotzer2005vars} is one of the earliest examples of VANET trust models, establishing a system called VARS, based on the reputation of nodes and messages throughout the network.
The authors use what they call \textit{opinion piggybacking}, which means that, for each hop between the origin and the destination of an event-related message, the forwarding node appends its opinion of the message's contents and the message's sender.
In other words, when a node $a$ receives a message about a certain event from $b$, it calculates a new opinion considering  it rebroadcasts the message to other nearby nodes, but with its own opinions about the event and about node $b$ attached.
%That opinion is formed using a combination of the forwarding node's own observations of the event, its opinion of the origin node and previous opinions appended to the message.
This process adds credibility to a message through validation by nodes in a decentralized fashion.
It combines aspect of data- and entity- based trust, since nodes share their opinion of the data as well as their opinion of the sender. 
An interesting observation is setting higher trust values for certain vehicles based on their familiarity with the region (vehicles that reside in a given city may have more experience with certain types of events than newcomers).
However, opinion piggybacking has its own share of problems.
First, it allows forwarding nodes to access (at least some of) the contents of a message so it can form an opinion on it, diminishing privacy; a malicious forwarding node could even attempt to alter those contents.
Second, since each new opinion appended to the message considers the previously appended opinions, the first nodes to forward the message to have a substantially greater impact over the final opinion than the later ones.
Finally, there is an issue with scalability, since appending new information to a message on each hop may add a significant overhead to the transmission. Additionally, the authors provide little to no experimentation or proof that their approach would be sound in a real-world network.

The model proposed in \citep{minhas2010towards} uses several criteria to judge whether or not a received message is trustworthy.
First, nodes are classified by their roles and previous experience with them.
Roles are used for vehicles which should be more trustworthy than the average: government official cars, traffic report vans, buses, cabs, etc.
Nodes also store their experience each time an event message is received (if one neighboring node reported an event which did not turn out to be true, its trust value is reduced).
Additionally, messages have higher reliability when their senders are closer in time and space to the reported event.
When several messages about the same event are received, a node can either choose the $n$ most trustworthy senders, according to the priority (fewer chosen nodes means a faster, but less precise, decision), or compute the majority opinion of the messages according to each sender's trust value.
The model considers both role-based trust and experience-based trust; although the work proposed here does not use role-based trust, the authors provide a useful method of calculating and updating an experience-based trust value, which might be used or adapted.
However, their model relies only on direct interaction between pairs of nodes, so no form of indirect trust (that is, trust values received from other nodes) is considered.

@@

In \citep{chen2010trust}, the authors propose to evaluate messages utilizing a cluster-based trust model.
By separating nodes into clusters with their geographical neighbors, it is possible to efficiently distribute the evaluation of messages using previously formed opinions.
When a node sends a message, one node in the cluster (the leader) must aggregate the other nodes' opinions on that message.
Afterward, the message is only forwarded to another cluster if that aggregate opinion is above a certain threshold; furthermore, nodes that receive the message only act upon it if the overall trust on it is above another threshold, which can be different according to the nature of the message.
However, it is unclear how the model behaves when the network is too sparse to form relevant clusters, neither do the authors inform how the aforementioned thresholds are decided.
Furthermore, maintaining clusters in a highly dynamic network is a costly job and, if the cluster leader itself is malicious, all the information from that cluster becomes untrustworthy.
%The whole premise of organizing a VANET in clusters is  
%The model considers role-based trust (i.e. static trust of pre-authenticated vehicles such as police units) and experience-based trust, which is calculated using knowledge of the outcomes related to previous messages.
%This model considers both role-based and experience-based trust.

The trust model in \citep{park2011long} takes advantage of daily commutes.
In this article, the focus is on the early stages of VANETs, in which a very small percentage of vehicles are equipped with OBUs.
To make trust viable in such a scenario, the authors rely on RSUs to store reputation information from passing vehicles.
Each vehicle must have an ``Agent RSU'', which is in charge of storing and sharing that vehicle's trust data to other passing vehicles and connected RSUs.
It must also keep the data updated when the vehicle approaches it again.
To make this viable, the properties of daily commutes are used: it is assumed that the vehicle is near its Agent RSU with reasonable frequency because it is located within the driver's home-to-work route.
The main problem with this model is that it relies on the presence of frequent RSUs, which might not always be viable.
It also does not make it clear what should happen when a vehicle stops using a route or does not have a daily predictable path (it does, however, handle occasions in which a vehicle chooses an alternate route or is absent for some days such as weekends and holidays).

The authors of \citep{huang2014social} take special note of two characteristics from social networks that can also be found in many VANET trust models: \textit{information cascading} and \textit{oversampling}.
That is, information reported by a number of original nodes (i.e. the ones that witnessed an event) may be diluted as nodes that forward it append their own opinions on the matter.
An algorithm is proposed to diminish that effect by assigning higher weights to the opinions of origin nodes and lower weights  to others.
However, the authors conclude that the optimal scenario is to assign no weight at all to forwarding nodes, therefore allowing each node to form an opinion based only on the original nodes' reports.
Furthermore, the authors are quick to dismiss the validity of entity-based trust, instead opting for a pure data-oriented approach.
%Since their model is based only on events, it also does not consider the usefulness of trust in more mundane cases such as the frequent sharing of location and speed among vehicles.
Although it is true that data-oriented trust is efficient for events, which is what their model is based on, it is not ideal for sharing data quickly and frequently.
When a collision or other major incident occurs, it is useful to judge each message on its own, since not all members of the network will have existing trust relationships with each other.
However, when sharing location and velocity data several times per second, it is not reasonable to expect that each message will be analyzed so carefully; rather, it makes sense to form an opinion about the sender of the message and use the resulting trust value to choose which messages are relevant or not.

The Attack-Resistant Trust Management Scheme (ART) from \citep{li2016art} proposes to resist three types of attacks: 
simple attacks, in which malicious nodes do not cooperate with the network;
bad-mouth attacks, in which malicious nodes perform simple attacks but also share false information about benign nodes;
and zig-zag attacks, in which nodes vary their behaviour from benign to malicious in order to be harder to detect.
It works in two main steps: data gathering and malicious node detection.
For data gathering, it uses the Dempster-Shafter theory of evidence, which establishes \textit{belief} and \textit{plausibility} values, both real numbers ranging from 0 to 1.
The former refers to the amount of evidence indicating the truthfulness of a hypothesis (for example, a node sending false data corroborates the hypothesis of it being malicious), while the latter is 1 minus the amount of evidence that supports the possibility of the hypothesis being false.
These evidences are acquired through observations by a node and through data received from other nodes.
The resulting probability is the basic trust value, which is stored in a trust vector (a series of trust values regarding other nodes).
The malicious node detection step uses a Cosine-based metric to compare two nodes' trust vectors.
When two nodes share similar opinions about other nodes, they will consider each other trustworthy.
The downside of this model is that each step is mathematically costly, requiring several intensive calculations in order to achieve its goals.
This likely increases the complexity of the algorithm, which is not detailed by the authors.
Because of this, it is uncertain how the model would scale to large networks, while it might also underperform in small networks in which there is little evidence to collect.
%The authors present no details on how it deals with sparsity, dynamics, scalability, security and privacy.
%extend

The authors of \citep{chen2017cloud} propose a cloud-based solution for a trust model, which requires an Internet-based global trust manager.
This has the advantage of simplifying properties such as handling sparsity and scalability, but also makes the system slower in general, especially in situations in which mobile communication is slow or unreliable.
In general, it goes against several established concepts for vehicular networks, such as being completely decentralized and ad-hoc.
It also makes the system somewhat, since the whole system collapses if the global trust manager is attacked, or could leave the network members unaided in the event of a server or connection failure.
%extend

%conclude
\Cref{table:properties} shows how well each studied trust model satisfies the eight properties described in \Cref{section:properties}.
The numbers used in the table are the same ones from \Cref{section:properties}.
This analysis shows that, although several previously proposed trust models provide reasonable solutions to the trust management problem, all of them have issues in terms of correctness, completeness or efficiency, indicating that the problem is not yet truly solved.

\begin{table}[t!]
\caption{Properties of the related work}
\label{table:properties}
\centering
\begin{tabular}{|p{4cm}||p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|}
 \hline
 \textbf{Property} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
 \hline
 \hline
% TruMan & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & - & \checkmark \\
% \hline
% \citep{vernize2015malicious} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
% \hline
 \citep{dotzer2005vars} & \checkmark & - & \checkmark & - & - & - & \checkmark & -\\
 \hline
 \citep{minhas2010towards} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -\\
 \hline
 \citep{chen2010trust} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & -\\
 \hline
 \citep{park2011long} & - & - & - & - & - & \checkmark & \checkmark & \checkmark \\
 \hline
 \citep{huang2014social} & \checkmark & - & \checkmark & \checkmark & \checkmark & - & - & -\\
 \hline
 \citep{li2016art} & \checkmark & - & - & - & \checkmark & - & - & \checkmark\\
 \hline
 \citep{chen2017cloud} & - & \checkmark & - & \checkmark & - & \checkmark & \checkmark & -\\
 \hline
\end{tabular}
\end{table}

>>>>

\section{Trust in Vehicular Ad-hoc Networks}
\label{chap:vanets}

@@

In traditional networks (ad-hoc or not), routing protocols usually use the topology to choose where to forward packets; in other words, the primary metric used is the number of hops required to reach the destination.
This metric is not as useful in vehicular networks, since the high mobility causes the topology to change frequently.
Instead, most VANET routing protocols use geographical coordinates to forward packets \citep{saini2015close}, that is, the physical distance between two nodes is used as the primary metric.
The implication is that, even if a packet requires more hops to reach its destination, it always travelling in the generally correct geographical direction.

@@

Like in other types of networks, the proper functioning of a VANET depends on the reliability of its participants.
If a node is malicious or faulty, it can spread incorrect data that may compromise the network's utility.
Once the concept of VANETs was established, researchers have been attempting to predict ways in which malicious users might use the network to their advantage.
Examples include triggering false alarms about inexistent accidents, lying about the average speed in a road to make it less desirable for others, and falsifying geolocation data to exploit location-based routing algorithms.
Therefore, the concept of trust must be established in the vehicular network context, allowing for nodes to judge the validity of information transmitted by others and share those conclusions with other nodes.

%[details of security and safety issues in VANETs that can be diminished by trust]

\subsection{Special properties of VANETs}
\label{section:properties}
%As was described above, VANETs are a special type of MANETs, which in turn are technological networks.
%However, 
VANETs feature several unique properties which distinguish them, and the behavior of its members, from other types of networks \citep{yousefi2006vehicular}.
Some of these properties include:

@@

%\subsection{Trust in VANETs}
%\label{section:trustvanet}

\subsection{Desired properties for VANET trust models}
\label{section:desired}

@@

\subsection{Existing trust models for VANETs}

@@

\citep{dotzer2005vars} is one of the earliest examples of VANET trust models, establishing a system called VARS, based on the reputation of nodes and messages throughout the network.
The authors use what they call \textit{opinion piggybacking}, which means that, for each hop between the origin and the destination of an event-related message, the forwarding node includes its opinion of the message's contents and the message's sender.
In other words, when a node $a$ receives a message about a certain event from $b$, it calculates a new opinion considering  it rebroadcasts the message to other nearby nodes, but with its own opinions about the event and about node $b$ attached.
%That opinion is formed using a combination of the forwarding node's own observations of the event, its opinion of the origin node and previous opinions appended to the message.
This process adds credibility to a message through validation by nodes in a decentralized fashion.
It combines aspect of data- and entity- based trust, since nodes share their opinion of the data as well as their opinion of the sender. 
An interesting observation is setting higher trust values for certain vehicles based on their familiarity with the region (vehicles that reside in a given city may have more experience with certain types of events than newcomers).
However, opinion piggybacking has its own share of problems.
First, it allows forwarding nodes to access (at least some of) the contents of a message so it can form an opinion on it, diminishing privacy; a malicious forwarding node could even attempt to alter those contents.
Second, since each new opinion appended to the message considers the previously appended opinions, the first nodes to forward the message to have a substantially greater impact over the final opinion than the later ones.
Finally, there is an issue with scalability, since appending new information to a message on each hop may add a significant overhead to the transmission. Additionally, the authors provide little to no experimentation or proof that their approach would be sound in a real-world network.

The model proposed in \citep{minhas2010towards} uses several criteria to judge whether or not a received message is trustworthy.
First, nodes are classified by their roles and previous experience with them.
Roles are used for vehicles which should be more trustworthy than the average: government official cars, traffic report vans, buses, cabs, etc.
Nodes also store their experience each time an event message is received (if one neighboring node reported an event which did not turn out to be true, its trust value is reduced).
Additionally, messages are considered more reliable when their senders were direct witnesses to an event (i.e. were close to the event when it happened).
When several messages about the same event are received, a node can either choose the $n$ most trustworthy senders, according to the priority of the event.
For example, events that require a fast response might cause a decision to be made using fewer messages about it, which diminishes precision.
% chosen nodes means a faster, but less precise, decision), or compute the majority opinion of the messages according to each sender's trust value.
The model considers both role-based trust and experience-based trust; although the work proposed here does not use role-based trust, the authors provide a useful method of calculating and updating an experience-based trust value, which might be used or adapted.
However, their model relies only on direct interaction between pairs of nodes, so no form of indirect trust (that is, trust values received from other nodes) is considered.

@@

In \citep{chen2010trust}, the authors propose to evaluate messages utilizing a cluster-based trust model.
By separating nodes into clusters with their geographical neighbors, it is possible to efficiently distribute the evaluation of messages using previously formed opinions.
When a node sends a message, one node in the cluster (the leader) must aggregate the other nodes' opinions on that message.
Afterward, the message is only forwarded to another cluster if that aggregate opinion is above a certain threshold; furthermore, nodes that receive the message only act upon it if the overall trust on it is above another threshold, which can be different according to the nature of the message.
However, it is unclear how the model behaves when the network is too sparse -- nodes are few and/or far apart -- to form relevant clusters, neither do the authors inform how the aforementioned thresholds are decided.
Furthermore, maintaining clusters in a highly dynamic network is a costly job and, if the node chosen to be the leader of a cluster happens to be malicious, all the information from that cluster could be compromised.
%The whole premise of organizing a VANET in clusters is  
%The model considers role-based trust (i.e. static trust of pre-authenticated vehicles such as police units) and experience-based trust, which is calculated using knowledge of the outcomes related to previous messages.
%This model considers both role-based and experience-based trust.

The trust model in \citep{park2011long} takes advantage of daily commutes.
In this article, the focus is on the early stages of VANETs, in which a very small percentage of vehicles are equipped with OBUs.
To make trust viable in such a scenario, the authors rely on RSUs to store reputation information from passing vehicles.
Each vehicle must have an ``Agent RSU'', which is in charge of storing and sharing that vehicle's trust data to other passing vehicles and connected RSUs.
It must also keep the data updated when the vehicle approaches it again.
To make this viable, the properties of daily commutes are used: it is assumed that the vehicle is near its Agent RSU with reasonable frequency because it is located within the driver's home-to-work route.
The main problem with this model is that it relies on the existence of a reasonably large number of RSUs, which might not always be viable due to infrastructure costs.
It also does not make it clear what should happen when a vehicle stops using a route or does not have a daily predictable path (it does, however, handle occasions in which a vehicle chooses an alternate route or is absent for some days such as weekends and holidays).

The authors of \citep{huang2014social} take special note of two characteristics from social networks that can also be found in many VANET trust models: \textit{information cascading} and \textit{oversampling}.
That is, information reported by a number of original nodes (i.e. the ones that witnessed an event) may be diluted as nodes that forward it append their own opinions on the matter.
Following the VARS \citep{dotzer2005vars} approach, an algorithm is proposed to diminish that effect by assigning higher weights to the opinions of nodes that were witnesses to an event and lower weights to forwarding nodes.
However, the authors conclude that the optimal scenario is to assign no weight at all to forwarding nodes, therefore allowing each node to form an opinion based only on the original nodes' reports.
Furthermore, the authors are quick to dismiss the validity of entity-based trust, instead opting for a pure data-oriented approach, considering only the contents of a message and disregarding who sent it.
%Since their model is based only on events, it also does not consider the usefulness of trust in more mundane cases such as the frequent sharing of location and speed among vehicles.
Although it is true that data-oriented trust is efficient for events, which is what their model is based on, it is not ideal for sharing data quickly and frequently.
When a collision or other major incident occurs, it is useful to judge each message on its own, since not all members of the network will have existing trust relationships with each other.
However, when sharing location and velocity data several times per second, it is not reasonable to expect that each message will be analyzed so carefully; rather, it makes sense to form an opinion about the sender of the message and use the resulting trust value to choose which messages are relevant or not.

The Attack-Resistant Trust Management Scheme (ART) from \citep{li2016art} proposes to resist three types of attacks: 
simple attacks, in which malicious nodes do not cooperate with the network;
bad-mouth attacks, in which malicious nodes perform simple attacks but also share false information about benign nodes;
and zig-zag attacks, in which nodes vary their behaviour from benign to malicious in order to be harder to detect.
It works in two main steps: data gathering and malicious node detection.
For data gathering, it uses the Dempster-Shafter theory of evidence, which establishes \textit{belief} and \textit{plausibility} values, both real numbers ranging from 0 to 1.
The former refers to the amount of evidence indicating the truthfulness of a hypothesis (for example, a node sending false data corroborates the hypothesis of it being malicious), while the latter is 1 minus the amount of evidence that supports the possibility of the hypothesis being false.
These evidences are acquired through observations by a node and through data received from other nodes.
The resulting probability is the basic trust value, which is stored in a trust vector (a series of trust values regarding other nodes).
The malicious node detection step uses a Cosine-based metric to compare two nodes' trust vectors.
When two nodes share similar opinions about other nodes, they will consider each other trustworthy.
The downside of this model is that each step is mathematically costly, requiring several intensive calculations in order to achieve its goals.
This likely increases the complexity of the algorithm, which is not detailed by the authors.
Because of this, it is uncertain how the model would scale to large networks, while it might also underperform in small networks in which there is little evidence to collect.
%The authors present no details on how it deals with sparsity, dynamics, scalability, security and privacy.

The authors of \citep{chen2017cloud} propose a cloud-based solution for a trust model, which requires an Internet-based global trust manager.
This has the advantage of simplifying properties such as handling sparsity and scalability, but also makes the system slower in general, especially in situations in which mobile communication is slow or unreliable.
In general, it goes against several established concepts for vehicular networks, such as being completely decentralized and ad-hoc.
It also makes the system somewhat unreliable, since the whole system collapses if the global trust manager is attacked, or could leave the network members unaided in the event of a server or connection failure.

\section{Discussion}
\label{section:background_discussion}

Analyzing the previous work in the subject of trust management for vehicular networks, it is possible to observe that many interesting solutions to the problem have been attempted, but all of them show at least one major deficiency when thinking about real-world implementation.
\Cref{table:properties} shows how well each studied trust model satisfies the eight properties described in \Cref{section:desired}, which are based on \citep{zhang2011survey}.
The numbers used in the table are the same ones from \Cref{section:desired}.

\begin{table}[hpbt!]
\caption{Properties of the related work}
\label{table:properties}
\centering
\begin{tabular}{|p{4cm}||p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|p{0.5cm}|}
 \hline
 \textbf{Property} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
 \hline
 \hline
% TruMan & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & - & \checkmark \\
% \hline
% \citep{vernize2015malicious} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8\\
% \hline
 \citep{dotzer2005vars} & \checkmark & - & \checkmark & - & - & - & \checkmark & -\\
 \hline
 \citep{minhas2010towards} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -\\
 \hline
 \citep{chen2010trust} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & - & -\\
 \hline
 \citep{park2011long} & - & - & - & - & - & \checkmark & \checkmark & \checkmark \\
 \hline
 \citep{huang2014social} & \checkmark & - & \checkmark & \checkmark & \checkmark & - & - & -\\
 \hline
 \citep{li2016art} & \checkmark & - & - & - & \checkmark & - & - & \checkmark\\
 \hline
 \citep{chen2017cloud} & - & \checkmark & - & \checkmark & - & \checkmark & \checkmark & -\\
 \hline
\end{tabular}
\end{table}

Furthermore, vehicular ad-hoc networks are a special kind of network, but, despite the unique properties explained in \Cref{section:properties}, they still share many features with mobile ad-hoc networks and even with social networks.

With this information in mind, a new trust model is introduced, taking advantage of social features in order to establish long-term trust relationships between participants of a vehicular ad-hoc network.
This new trust model emphasizes efficiency while maintaining correctness and most of the desired properties for such a model.
In the following chapter, the model is explained in detail.
%This analysis shows that, although several previously proposed trust models provide reasonable solutions to the trust management problem, all of them have issues in terms of correctness, completeness or efficiency, indicating that the problem is not yet truly solved.

### 2018-07-04 dissertation/4-project/chapter4.tex
Updated chapter 2

\chapter{TruMan}
\label{chap:truman}

@@

>>>>

\chapter{Design and Implementation of TruMan}
\label{chap:truman}

@@

\section{Discussion}
\label{section:truman_discussion}

This chapter shows the concepts and algorithms that went into the development of TruMan.
Using efficient algorithms as a foundation, TruMan is able to efficiently detect and identify malicious nodes operating within a dynamic network.

Although TruMan could be a viable solution for multiple kinds of networks, this work is focused primarily on vehicular networks and, therefore, TruMan was developed with such networks in mind.
The following chapter explains how TruMan was evaluated in the context of vehicular networks, including results of the performed experiments.

### 2018-07-04 dissertation/5-simulations/chapter5.tex
Updated chapter 2

\section{SNAP library}
\label{section:snap}
The simulations necessary to validate the project require a robust library to handle graph data structures.
The Stanford Network Analysis Platform (SNAP) library \citep{snap} was chosen primarily because it is memory efficient.
The simulations require multiple graphs that share the same set of nodes (because each node in the network has its own knowledge of the surrounding network), and the SNAP library uses pointers to nodes and edges, saving memory by not having to duplicate the entire data structure.
It is written in C++, but, for these simulations, the Snap.py Python library was used.

%The datasets available from SNAP's website were used for the simulations in \citep{vernize2015malicious} and the static network simulations shown in \Cref{chap:simulations}.

\section{The ONE Simulator}
\label{section:theone}
The Opportunistic Network Environment simulator \citep{keranen2009one} \citep{onerepo} is a Delay-Tolerant Network simulator, used in this study to generate mobility patterns used as input for simulations.
It was chosen for the simulations of TruMan primarily because it already includes integration with the Working Day Movement Model.

>>>>

\section{Tools}
\label{section:tools}

\textbf{SNAP library}

The simulations necessary to validate the project require a robust library to handle graph data structures.
The Stanford Network Analysis Platform (SNAP) library \citep{snap} was chosen primarily because it is memory efficient.
The simulations require multiple graphs that share the same set of nodes (because each node in the network has its own knowledge of the surrounding network), and the SNAP library uses pointers to nodes and edges, saving memory by not having to duplicate the entire data structure.
It is written in C++, but, for these simulations, the Snap.py Python library was used.

%The datasets available from SNAP's website were used for the simulations in \citep{vernize2015malicious} and the static network simulations shown in \Cref{chap:simulations}.
%\\
\textbf{The ONE Simulator}

The Opportunistic Network Environment simulator \citep{keranen2009one} \citep{onerepo} is a Delay-Tolerant Network simulator, used in this study to generate mobility patterns used as input for simulations.
It was chosen for the simulations of TruMan primarily because it already includes integration with the Working Day Movement Model.
